API design for machine learning software: experiences from the scikit-learn project

### 2013-10-19 paper.tex
Typos

The code in Figure~\ref{svm-gridsearch} shows how to find
hyper-parameter settings for an support vector classifier (SVC)
that maximize $F_1$ score
through 10-fold cross-validation on the training set.
Two distinct hyper-parameter grids are
considered for the linear and radial basis function (RBF) kernels;
an SVC with a linear kernel accepts a $\gamma$ parameter, but ignores it,
so using a single parameter grid would waste computing time
trying out effectively equivalent settings.

@@

Our rule of thumb is that user code should not be tied to \sklearn---which is a
\textit{library}, not a framework. We try to avoid a
common problem with object-oriented design: that users wanting a
``banana'' instead get ``a gorilla holding the banana and the entire jungle''
(J.~Armstrong, cited in \citep[p.~213]{seibel2009coders}).
Programs using \sklearn should not be intimately tied to it,
so that their code can be reused or in other contexts.

>>>>

The code in Figure~\ref{svm-gridsearch} shows how to find
hyper-parameter settings for a support vector classifier (SVC)
that maximizes $F_1$ score
through 10-fold cross-validation on the training set.
Two distinct hyper-parameter grids are
considered for the linear and radial basis function (RBF) kernels;
an SVC with a linear kernel accepts a $\gamma$ parameter, but ignores it,
so using a single parameter grid would waste computing time
trying out effectively equivalent settings.

@@

Our rule of thumb is that user code should not be tied to \sklearn -- which is a
\textit{library}, not a framework. We try to avoid a
common problem with object-oriented design: that users wanting a
``banana'' instead get ``a gorilla holding the banana and the entire jungle''
(J.~Armstrong, cited in \citep[p.~213]{seibel2009coders}).
Programs using \sklearn should not be intimately tied to it,
so that their code can be reused in other contexts.
